The growth of children's semantic and phonological networks: insight from 10 languages

### 2019-09-23 journal/ms.tex
new version

What factors shape vocabulary learning over the course of early
childhood? To investigate this question, scientists have adopted
multiple research strategies, from conducting controlled laboratory
experiments (e.g. Markman, 1990) to analyzing dense corpora capturing
language learning in context (e.g., B. C. Roy, Frank, DeCamp, Miller, \&
Roy, 2015). One prominent strategy consists in documenting the timeline
of words' acquisition, and studying the properties that make words easy
or hard to learn (e.g., J. C. Goodman, Dale, \& Li, 2008; Huttenlocher,
Haight, Bryk, Seltzer, \& Lyons, 1991). For example, J. C. Goodman et
al. (2008) found that, within a lexical category (e.g., nouns), higher
parental frequency is associated with earlier learning. Researchers have
studied the role of several other factors such as word length and the
mean length of utterances in which the word occurs (e.g., Braginsky,
Yurovsky, Marchman, \& Frank, 2019; D. Swingley \& Humphrey, 2018).

Besides word-level properties, the structure of the lexicon (that is,
how words relate to one another) is also linked to the the Age of
Acquisition (AoA) of words. The lexical structure can be characterized
in terms of a network where each node represents a word in the
vocabulary, and each link between two nodes represents a relationship
between the corresponding pair of words (e.g., Collins \& Loftus, 1975;
Luce \& Pisoni, 1998). Previous studies have investigated early
vocabulary structure by constructing networks using a variety of
word-word relations including shared semantic features (McRae, Cree,
Seidenberg, \& McNorgan, 2005), target-cue relationships in free
association norms (Nelson, McEvoy, \& Schreiber, 1998), co-occurrence in
child directed speech (MacWhinney, 2014), and phonological relatedness
(Vitevitch, 2008). These studies have generally found that children tend
to produce words that have higher neighborhood density (i.e., high
connectivity in the network) earlier, both at the phonological and the
semantic level (Carlson, Sonderegger, \& Bane, 2014; Hills, Maouene,
Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \& Smith, 2009;
Stella, Beckage, \& Brede, 2017; Storkel, 2009).

@@

These two proposals represent two divergent ideas about the role of
lexical networks in acquisition. On the INT proposal, learning is driven
by known words with high connectivity to other known words (Figure 1,
left). Thus, the network structure is a causal factor in word learning,
that is, children rely on the organization of their past knowledge to
determine future learning (Altvater-Mackensen \& Mani, 2013; Borovsky,
Ellis, Evans, \& Elman, 2016; Chi \& Koeske, 1983; Storkel, 2009). In
contrast, on the EXT approach, learning is driven by the connectivity of
words that are not known yet (Figure 1, right). Thus, the relevant
network structure is not internally represented by children, and the
observed connectivity effect might be an epiphenomenon of some
properties of the linguistic input. For example, highly connected
concrete nouns in the input could be more easily learned because of
their contextual diversity, allowing for an easier meaning
disambiguation (McMurray, Horst, \& Samuelson, 2012; Smith \& Yu, 2008;
Yurovsky \& Frank, 2015). Another reason could be that these words are
emphasized by the caregivers in their child-directed speech (Clark,
2007; Hoff \& Naigles, 2002; Huttenlocher et al., 1991).

@@

\caption{Illustration of the two growth scenarios. Filled grey circles represent known words (Internal) at a certain point in time. The empty, numbered circles represent words that have not yet been learned (External) and which are candidates to enter the lexicon next. The identity of the word that is going to be learned depends on the growth scenario.  Here the squares indicate the node that drives growth in each scenario and the hand pointer indicates which word is likely to be learned. For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. In this simplified example, candidate node 1 would connect to an internal node with 3 connections, thus we have $u_{INT}(node_1)= 3$. As for candidate node 2, it would connect to internal nodes that have only one connection each, making an average of 1, i.e., $u_{INT}(node_2)= 1$. According to INT, node 1 is more likely to enter the lexicon. For EXT, the utility of a candidate node is its degree in the entire network. In our example, candidate node 1 has 2 connections in total whereas candidate node 2 has 5 connections. So we have $u_{EXT}(node_1)= 2$ and $u_{EXT}(node_2)= 5$. Thus, according to EXT, node 2 is more likely to enter the lexicon next. This figure is based on an example from Hills et al. (2009).}\label{fig:growth}
\end{figure}

@@

First, we study the phonological network in addition to the semantic
network. These two networks represent different ways the mental lexicon
is structured (Beckage \& Colunga, 2016). In particular, words that are
neighbors in the semantic network (e.g., \enquote{cat}, \enquote{dog})
are not necessarily neighbors in the phonological network, and vice
versa. Does the phonological network also predict word learning?
Previous work has found an effect of words' connectivity in the
phonological network on their age of learning (Carlson et al., 2014;
Stella et al., 2017; Storkel, 2009). In other words, words learned
earlier in life tend to sound similar to many other words than a word
learned later in life. However, this finding is \emph{a priori}
compatible with both INT and EXT, and previous studies did not
explicitly compare these two mechanisms. Here, we investigate whether
phonological networks, like semantic networks, grow through EXT, or if
they rather grow via INT (Figure~\ref{fig:growth}).

@@

We adopted the following research strategy. We used parent reports on
the MacArthur-Bates Communicative Development Inventory and its
cross-linguistic adaptations (Fenson et al., 1994; Frank, Braginsky,
Yurovsky, \& Marchman, 2017). We studied the timeline of word learning
using the normative age of acquisition (i.e., the age at which at least
50\% of children know a given words). Our choice of studying the
normative learning trajectory rather than the individual trajectories
was motivated by the nature of the dataset used---which is primarily
based on cross-sectional studies. Children may vary in their individual
learning trajectories, but the aggregate data provide highly robust
measures of the average learning patterns (Fenson et al., 1994). The use
of such measures has lead to important insights on the mechanisms of
word learning (J. C. Goodman et al., 2008; Hills et al., 2010, 2009;
Stella et al., 2017; Storkel, 2009).

The paper is organized as follows. First, we describe the datasets we
used and explain how we constructed the networks. Second, we analyze
static properties of words' connectivity in these networks (correlation
with age of acquisition and shape of the distribution) and we explain
how these properties inform hypotheses about network growth. Next, we
fit the two hypothesized growth mechanisms to the data. We investigate
the extent to which the results obtained in Hills et al. (2009)
generalize to phonological networks and comprehension-based
vocabularies, and whether this generalization holds
cross-linguistically.

@@

We constructed semantic networks for English data following the
procedure outlined in Hills et al. (2009), as follows. We used as an
index of semantic relatedness the Florida Free Association Norms (Nelson
et al., 1998). This dataset was collected by giving adult participants a
word (the cue), and asking them to write the first word that comes to
mind (the target). For example, when given the word \enquote{ball}, they
might answer with the word \enquote{game}. A pair of nodes were
connected by a directed link from the cue to the target if there was a
cue-target relationship between these nodes in the association norms.
The connectivity of a given node was characterized by its
\emph{indegree}: the number of links for which the word was the
target.\footnote{This choice was based on prior work by Hills et al. (2009) stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated with indegree.}
To model growth from month to month, we constructed a different network
at each month, based on the nouns that have been acquired by that month.

Since the free association norms are available only in English, we used
the hand-checked translation equivalents available in Wordbank, which
allowed us to use the English association norms across 10 languages.
Semantic associations are not necessarily shared across languages, but
we use this technique as a reasonable first approximation. In support of
this approximation, Youn et al. (2016) showed that semantic networks
across languages share substantial similarities. Furthermore, using the
same association data across languages does not necessarily mean that
the resulting networks will grow in a similar fashion. For instance, the
set of words acquired by children as well as the order of word
acquisition can vary from language to language leading to possibility
different learning strategies.

@@

To construct phonological networks we first mapped the orthographic
transcription of words to their International Phonetic Alphabet (IPA)
transcriptions in each language, using the open source text-to-speech
software \textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}}.
This software provides the correct IPA transcription if the word is
found in a spelling-to-phonemes dictionary, otherwise it uses
language-specific pronunciation rules to generate an approximate
phonetic transcription. We used the Levenshtein distance (also known as
edit distance) as a measure of phonological relatedness between two
nodes. The measure counts the minimum number of operations (insertions,
deletions, substitutions) required to change one string into another.

In previous studies, two nodes were linked if they had an edit distance
of 1 (Carlson et al., 2014; Stella et al., 2017; Storkel, 2009).
However, these studies reported a contribution of phonological
connectivity to noun learning when networks were built using a rich
adult vocabulary. Since the focus of the current study is on the
mechanism of growth, the networks should be based on children's early
vocabulary. The latter, however, contains very few noun pairs with an
edit distance of 1. Thus, we increased the threshold from 1 to 2, that
is, two nodes were related if their edit distance was equal to 1 or
2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold. In both cases, the results were weaker than those obtained with a threshold of 2. We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").}
The connectivity of a given node was characterized with its
\emph{degree}: the number of links it shares with other words.

@@

In brief, the analysis consisted in two steps. First, we derived the
optimal cut-off, \(k_{min}\), above which the distribution is more
likely to follow a power
law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
and we estimate the corresponding scaling parameter \(\alpha\). Second
we calculated the goodness-to-fit, which resulted in a \(p\)-value
quantifying the plausibility of the model. The results are shown in
Table \ref{tab:powerLawProd} for production data, and in Table
\ref{tab:powerLawComp} for comprehension data.

@@

\noindent where \(\beta\) is a fitted parameter that captures the
magnitude of the relationship between network parameters and growth
(analogous to a regression coefficient). A positive value of \(\beta\)
means that words with higher utility values \(u_i\) are acquired first,
and a negative value means that words with lower utility values are
acquired first (see Figure \ref{fig:growth} for an illustration of how
utilities values \(u_i\) are defined in each growth scenario). The
normalization includes all words that could be learned at that month.

We estimated the parameter \(\beta\) using a Bayesian approach. The
inference was performed using the probabilistic programming language
WebPPL (N. Goodman \& Stuhlmuller, 2014). We defined a uniform prior
over \(\beta\), and at each month, we computed the likelihood function
over words that could possibly enter the lexicon at that month, fit to
the words that have been learned at that month (using Formula 1). Markov
Chain Monte Carlo sampling resulted in a posterior distribution over
\(\beta\), which we summarized in Figure \ref{fig:growthPred}. The
results replicate Hills et al.'s original finding regarding the semantic
network in English and the production-based vocabulary, which is that
this network grows by EXT, not by INT. Crucially, our results show that,
generally speaking, this finding generalizes to comprehension-based
vocabulary, and holds across languages. This generalization was obtained
in both the semantic\footnote{One could imagine that the fact of using
  English free association norms cross-linguistically would decrease the
  effect of non-English semantic networks because of possible cultural
  differences. However, our findings do not support this assumption,
  rather, it supports our initial approximation about the shared nature
  of the semantic similarity measure. That said, this approximation is
  not perfect. For example there is evidence that a small part of the
  variance in free association data can be explained by phonological
  similarity (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson,
  2018), thus leading to possibly minor cross-linguistic differences.}
and phonological domains.

@@

Above we showed that the way semantic and phonological information is
structured in the learning environment contributes to noun learning (via
EXT) across languages. However, we know that other factors influence
learning as well (e.g., Braginsky et al., 2019). Next we investigated
how semantic and phonological connectivity interact with two other
factors. The first one is word frequency, a well studied factor shown to
predict the age of acquisition in a reliable fashion (e.g. J. C. Goodman
et al., 2008). The second factor is word length, which was shown to
correlate with phonological connectivity: Shorter words are more likely
to have higher connectivity (Pisoni, Nusbaum, Luce, \& Slowiaczek, 1985;
Vitevitch \& Rodríguez, 2005).

Since we found INT to be uninformative, we dropped it from this
analysis, keeping only EXT. This simplified the model because we no
longer needed to fit growth month-by-month. The latter was a requirement
only for INT where the words' utilities varied from month to month,
depending on how connectivity changed in the growing internal network. A
more direct way to assess and compare the contribution of EXT in
relation to other word-level factors is through conducting regressions,
where connectivity in the learning environment, frequency and length
predict the age of acquisition.

@@

For example, in the semantic domain, growth according to EXT could be
explained by a mechanism similar to cross-situational learning (McMurray
et al., 2012; Smith \& Yu, 2008; Yurovsky \& Frank, 2015). According to
this mechanism, children track the co-occurrence of concrete nouns with
their possible semantic referents. The referent of a word heard in only
one naming situation can be ambiguous (e.g., when the word
\enquote{ball} is heard for the first time in the presence of both a
ball and a chair), but hearing the same word in a diversity of semantic
contexts allows the learner to narrow down the set of possible
word-object mappings. In our case, free association (used to determine
semantic network connectivity) is related to contextual co-occurrence
(Fourtassi \& Dupoux, 2013; Griffiths, Steyvers, \& Tenenbaum, 2007),
meaning that highly connected words will tend to occur in a variety of
speech and referential contexts. This fact makes such words easier to
learn because they have more referential disambiguating cues across
learning contexts. Crucially, children can learn these words without
necessarily knowing the meaning of all other words with which they
co-occur (hence the similarity with EXT). This possibility is supported
by the finding that words' diversity of occurrence in child directed
speech predicts their age of learning (Hills et al., 2010; Stella et
al., 2017).

In the phonological case, network growth according to EXT is also
compatible with a scenario whereby children are tracking low level
statistical patterns, e.g., high probability sound sequences. Indeed,
connectivity in the phonological network is inherently correlated with
phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
is, highly connected words tend to be made of frequent sound sequences.
Children are sensitive to local phonotactic regularities (Jusczyk, Luce,
\& Charles-Luce, 1994) and this sensitivity might lead them to learn
higher-probability words more easily (Storkel, 2001). This explanation
is supported by computational simulations that show how learning general
phonotactics patterns create \enquote{well-worn paths} which allow the
models to represent several distinct but phonologically neighboring
words (Dell, Juliano, \& Govindjee, 1993; Siew, 2013; Takac, Knott, \&
Stokes, 2017). More generally, there is a growing interest in
investigating precisely how the local patterns acquired through
statistical learning may give rise to the global network orgnization
(For a review, see Karuza, Thompson-Schill, \& Bassett, 2016).

Besides using their own statistical learning skills, children could also
benefit from the way their caregivers speak. Perhaps the caregivers put
more emphasis on the words that are highly connected in \emph{their}
mature lexical network. This emphasis would guide children to learn
first these highly connected words even though children do not have
access to the distribution of words' connectivity in the final network.
Investigating this possibility would require further research on
caregiver-child interaction (MacWhinney, 2014; B. C. Roy et al., 2015),
examining what words are introduced over development and the extent to
which children's uptake is influenced by this input (Clark, 2007; Hoff
\& Naigles, 2002; Huttenlocher et al., 1991).

This study investigated the class of nouns in isolation --- following
previous studies investigating the early semantic and phonological
network (Hills et al., 2009; Storkel, 2009). We could ask if studying
one class separtaly is a legitimate research strategy. In other words,
would word classes (such as nouns, verbs and function words) be acquired
relatively differently, or would they interact substantially to the
extent that it becomes unreasonable to study each class separately?

We know that different word classes follow different time trajectories.
For instance, in the early stages of development, nouns tend to be
acquired at a higher pace than predicates and function words (Bates et
al., 1994). Research has shown that this difference cannot be trivially
attributed to differences in the degree to which these classes are
present in the input; if anything, verbs and function words are often
more frequent in the input than nouns (e.g., Gentner, 1982). J. C.
Goodman et al. (2008) found an effect of frequency on the age of
acquisition within --- not across --- classes. Further, a recent work by
Braginsky et al. (2019) tested a large number of predictors, besides
frequency, and found that these predictors do not influence the
acquisition of word classes in the same way. For example, the
acquisition of nouns was found to be most influenced by frequency and
concreteness, whereas the acquisition of function words was most
influenced by word length.

These patterns support the hypothesis that different word classes have
different pathways of learning, thus making it worthwhile to study each
class separately. This hypothesis, however, does not preclude all sorts
of inter-class interaction. For example, Dautriche, Swingley, and
Christophe (2015) found that the acquisition of similar-sounding words
(\enquote{bih}-\enquote{dih}) is easier if these words belong to
different syntactic categories (e.g., a noun and a verb).

This work shares a number of limitations with previous studies using
similar research strategy and datasets. Chief among these limitations is
the fact that the age of word acquisition is computed using different
children at different ages (due to the fact that available CDI data is
mainly cross-sectional). Such a measure has been shown to be valid and
reliable (Fenson et al., 1994), and has allowed researchers to study
important aspects of word learning (Braginsky et al., 2019; J. C.
Goodman et al., 2008; Hills et al., 2009; Stella et al., 2017; Storkel,
2009). In our case, the use of cost-effective cross-sectional data has
allowed us to leverage large-scale studies across several languages.
That said, it is important to remember that this type of data can only
inform us about the learning trajectory of the \enquote{average} child.
Although our study endorses, overall, the externally-driven account of
network growth, this does not mean individual children never use some
variant of INT or some combination of both INT and EXT (Beckage \&
Colunga, under review). To illustrate, some children develop
\enquote{islands of expertise}, that is, well organized knowledge about
a certain topic (e.g., birds or dinosaurs). This prior knowledge enables
these children to learn new related words more easily (e.g., Chi \&
Koeske, 1983).

@@

We show in Figure \ref{fig:corrPlot} the correlation between the
phonological connectivity and age of acquisition in both comprehension
and production. The sparsity issue, due the low phonological
neighborhood in the children's lexicon is apparent: most words had 0
degree and a few had non-zero but small degrees. The values of the
correlations are much lower than the ones obtained with the threshold of
2.

>>>>

What factors shape vocabulary learning over the course of early
childhood? To investigate this question, scientists have adopted
multiple research strategies, from conducting controlled laboratory
experiments (e.g. Markman, 1990) to analyzing dense corpora capturing
language learning in context (e.g., B. C. Roy, Frank, DeCamp, Miller, \&
Roy, 2015). One prominent strategy consists in documenting the timeline
of words' acquisition and studying the properties that make words easy
or hard to learn (e.g., J. C. Goodman, Dale, \& Li, 2008; Huttenlocher,
Haight, Bryk, Seltzer, \& Lyons, 1991). For example, J. C. Goodman et
al. (2008) found that, within a lexical category (e.g., nouns), higher
parental frequency is associated with earlier learning. Researchers have
studied the role of several other factors such as word length and the
mean length of utterances in which the word occurs (e.g., Braginsky,
Yurovsky, Marchman, \& Frank, 2019; Swingley \& Humphrey, 2018).

Besides word-level properties, the structure of the lexicon (that is,
how words relate to one another) is also linked to the Age of
Acquisition (AoA) of words. The lexical structure can be characterized
in terms of a network where each node represents a word in the
vocabulary, and each link between two nodes represents a relationship
between the corresponding pair of words (e.g., Collins \& Loftus, 1975;
Luce \& Pisoni, 1998). Previous studies have investigated early
vocabulary structure by constructing networks using a variety of
word-word relations including shared semantic features (McRae, Cree,
Seidenberg, \& McNorgan, 2005), target-cue relationships in free
association norms (Nelson, McEvoy, \& Schreiber, 1998), co-occurrence in
child-directed speech (MacWhinney, 2014), and phonological relatedness
(Vitevitch, 2008). These studies have generally found that children tend
to produce words that have higher neighborhood density (i.e., high
connectivity in the network) earlier, both at the phonological and the
semantic level (Carlson, Sonderegger, \& Bane, 2014; Hills, Maouene,
Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya, \& Smith, 2009;
Stella, Beckage, \& Brede, 2017; Storkel, 2009).

@@

These two proposals represent two divergent ideas about the role of
lexical networks in acquisition. On the INT proposal, learning is driven
by known words with high connectivity to other known words (Figure 1,
left). Thus, the network structure is a causal factor in word learning,
that is, children rely on the organization of their past knowledge to
determine future learning (Altvater-Mackensen \& Mani, 2013; Borovsky,
Ellis, Evans, \& Elman, 2016; Chi \& Koeske, 1983; Storkel, 2009). In
contrast, on the EXT approach, learning is driven by the connectivity of
words that are not known yet (Figure 1, right). Thus, the relevant
network structure is not internally represented by children, and the
observed connectivity effect might be an epiphenomenon of some
properties of the linguistic input. For example, highly connected
concrete nouns in the input could be more easily learned because of
their contextual diversity, allowing for easier meaning disambiguation
(McMurray, Horst, \& Samuelson, 2012; Smith \& Yu, 2008; Yurovsky \&
Frank, 2015). Another reason could be that these words are emphasized by
the caregivers in their child-directed speech (Clark, 2007; Hoff \&
Naigles, 2002; Huttenlocher et al., 1991).

@@

\caption{Illustration of the two growth scenarios. Filled grey circles represent known words (Internal) at a certain point in time. The empty, numbered circles represent words that have not yet been learned (External) and which are candidates to enter the lexicon next. The identity of the word that is going to be learned depends on the growth scenario.  Here the squares indicate the node that drives growth in each scenario, and the hand pointer indicates which word is likely to be learned. For INT, the utility of a candidate external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. In this simplified example, candidate node 1 would connect to an internal node with 3 connections; thus we have $u_{INT}(node_1)= 3$. As for candidate node 2, it would connect to internal nodes that have only one connection each, making an average of 1, i.e., $u_{INT}(node_2)= 1$. According to INT, node 1 is more likely to enter the lexicon. For EXT, the utility of a candidate node is its degree in the entire network. In our example, candidate node 1 has 2 connections in total, whereas candidate node 2 has 5 connections. So we have $u_{EXT}(node_1)= 2$ and $u_{EXT}(node_2)= 5$. Thus, according to EXT, node 2 is more likely to enter the lexicon next. This figure is based on an example from Hills et al. (2009).}\label{fig:growth}
\end{figure}

@@

First, we study the phonological network in addition to the semantic
network. These two networks represent different ways the mental lexicon
is structured (Beckage \& Colunga, 2016). In particular, words that are
neighbors in the semantic network (e.g., cat, dog) are not necessarily
neighbors in the phonological network and vice versa. Does the
phonological network also predict word learning? Previous work has found
an effect of words' connectivity in the phonological network on their
age of learning (Carlson et al., 2014; Stella et al., 2017; Storkel,
2009). In other words, words learned earlier in life tend to sound
similar to many other words than a word learned later in life. However,
this finding is \emph{a priori} compatible with both INT and EXT, and
previous studies did not explicitly compare these two mechanisms. Here,
we investigate whether phonological networks, like semantic networks,
grow through EXT, or if they rather grow via INT
(Figure~\ref{fig:growth}).

@@

We adopted the following research strategy. We used parent reports on
the MacArthur-Bates Communicative Development Inventory and its
cross-linguistic adaptations (Fenson et al., 1994; Frank, Braginsky,
Yurovsky, \& Marchman, 2017). We studied the timeline of word learning
using the normative age of acquisition (i.e., the age at which at least
50\% of children know a given word). Our choice of studying the
normative learning trajectory rather than the individual trajectories
was motivated by the nature of the dataset used---which is primarily
based on cross-sectional studies. Children may vary in their individual
learning trajectories, but the aggregate data provide highly robust
measures of the average learning patterns (Fenson et al., 1994). The use
of such measures has lead to important insights on the mechanisms of
word learning (J. C. Goodman et al., 2008; Hills et al., 2010, 2009;
Stella et al., 2017; Storkel, 2009).

The paper is organized as follows. First, we describe the datasets we
used and explain how we constructed the networks. Second, we analyze
static properties of words' connectivity in these networks (correlation
with age of acquisition and shape of the distribution), and we explain
how these properties inform hypotheses about network growth. Next, we
fit the two hypothesized growth mechanisms to the data. We investigate
the extent to which the results obtained in Hills et al. (2009)
generalize to phonological networks and comprehension-based
vocabularies, and whether this generalization holds
cross-linguistically.

@@

We constructed semantic networks for English data following the
procedure outlined in Hills et al. (2009), as follows. We used as an
index of semantic relatedness the Florida Free Association Norms (Nelson
et al., 1998). This dataset was collected by giving adult participants a
word (the cue), and asking them to write the first word that comes to
mind (the target). For example, when given the word \enquote{ball,} they
might answer with the word \enquote{game.} A pair of nodes were
connected by a directed link from the cue to the target if there was a
cue-target relationship between these nodes in the association norms.
The connectivity of a given node was characterized by its
\emph{indegree}: the number of links for which the word was the
target.\footnote{This choice was based on prior work by Hills et al. (2009) stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated with indegree.}
To model growth from month to month, we constructed a different network
at each month, based on the nouns that have been acquired by that month.

Since the free association norms are available only in English, we used
the hand-checked translation equivalents available in Wordbank, which
allowed us to use the English association norms across 10 languages.
Semantic associations are not necessarily shared across languages, but
we use this technique as a reasonable first approximation. In support of
this approximation, Youn et al. (2016) showed that semantic networks
across languages share substantial similarities. The fact that semantic
associations are assumed to be shared across languages does not mean
that the semantic networks will necessarily grow in a similar fashion.
For instance, the set of words acquired by children as well as the order
of word acquisition can vary from language to language leading to
possibily different learning strategies.

@@

To construct phonological networks we first mapped the orthographic
transcription of words to their International Phonetic Alphabet (IPA)
transcriptions in each language, using the open-source text-to-speech
software \textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}}.
This software provides the correct IPA transcription if the word is
found in a spelling-to-phonemes dictionary, otherwise it uses
language-specific pronunciation rules to generate an approximate
phonetic transcription. We used the Levenshtein distance (also known as
edit distance) as a measure of phonological relatedness between two
nodes. The measure counts the minimum number of operations (insertions,
deletions, substitutions) required to change one string into another.

In previous studies, two nodes were linked if they had an edit distance
of 1 (Carlson et al., 2014; Stella et al., 2017; Storkel, 2009).
However, these studies reported a contribution of phonological
connectivity to noun learning when networks were built using a dense
adult vocabulary. Since the focus of the current study is on the
mechanism of growth, the networks are based on children's early
vocabulary. The latter, however, contains very few noun pairs with an
edit distance of 1. To better represent the similarity space in the
phonological domain, we increased the threshold from 1 to 2, that is,
two nodes were related if their edit distance was equal to 1 or
2.\footnote{In Appendix A, we show the main results for phonological networks based on an edit distance of 1. We also show the results for phonological networks where the edges between pairs of words were weighted by the inverse of the edit distance. We did not consider the case of a threshold larger than 2 since many short pairs appear phonologically unrelated when the edit distance is 3 or more (e.g., "cat"/"dog").}
The connectivity of a given node was characterized with its
\emph{degree}: the number of links it shares with other words.

@@

In brief, the analysis consisted in two steps. First, we derived the
optimal cut-off, \(k_{min}\), above which the distribution is more
likely to follow a power
law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
and we estimate the corresponding scaling parameter \(\alpha\). Second,
we calculated the goodness-to-fit, which resulted in a \(p\)-value
quantifying the plausibility of the model. The results are shown in
Table \ref{tab:powerLawProd} for production data, and in Table
\ref{tab:powerLawComp} for comprehension data.

@@

\noindent where \(\beta\) is a fitted parameter that captures the
magnitude of the relationship between network parameters and growth
(analogous to a regression coefficient). A positive value of \(\beta\)
means that words with higher utility values \(u_i\) are acquired first,
and a negative value means that words with lower utility values are
acquired first (see Figure \ref{fig:growth} for an illustration of how
utility values \(u_i\) are defined in each growth scenario). The
normalization includes all words that could be learned at that month.

We estimated the parameter \(\beta\) using a Bayesian approach. The
inference was performed using the probabilistic programming language
WebPPL (N. Goodman \& Stuhlmuller, 2014). We defined a uniform prior
over \(\beta\), and at each month, we computed the likelihood function
over words that could possibly enter the lexicon at that month, fit to
the words that have been learned at that month (using Formula 1). Markov
Chain Monte Carlo sampling resulted in a posterior distribution over
\(\beta\), which we summarized in Figure \ref{fig:growthPred}. The
results replicate Hills et al.'s original finding regarding the semantic
network in English and the production-based vocabulary, which is that
this network grows by EXT, not by INT. Crucially, our results show that,
generally speaking, this finding generalizes to comprehension-based
vocabulary, and holds across languages. This generalization was obtained
in both the semantic\footnote{One could imagine that the fact of using
  English free association norms cross-linguistically would decrease the
  effect of non-English semantic networks because of possible cultural
  differences. However, our findings do not support this assumption;
  rather, it supports our initial approximation about the shared nature
  of the semantic similarity measure. That said, this approximation is
  not perfect. For example, there is evidence that a small part of the
  variance in free association data can be explained by phonological
  similarity (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson,
  2018), thus leading to possibly minor cross-linguistic differences.}
and phonological domains.

@@

Above we showed that the way semantic and phonological information is
structured in the learning environment contributes to noun learning (via
EXT) across languages. However, we know that other factors influence
learning as well (e.g., Braginsky et al., 2019). Next, we investigated
how semantic and phonological connectivity interact with two other
factors. The first one is word frequency, a well-studied factor shown to
predict the age of acquisition in a reliable fashion (e.g., J. C.
Goodman et al., 2008). The second factor is word length, which was shown
to correlate with phonological connectivity: Shorter words are more
likely to have higher connectivity (Pisoni, Nusbaum, Luce, \&
Slowiaczek, 1985; Vitevitch \& Rodríguez, 2005).

Since we found INT to be uninformative, we dropped it from this
analysis, keeping only EXT. This simplified the model because we no
longer needed to fit growth month-by-month. The latter was a requirement
only for INT where the words' utilities varied from month to month,
depending on how connectivity changed in the growing internal network. A
more direct way to assess and compare the contribution of EXT in
relation to other word-level factors is through conducting regressions,
where connectivity in the learning environment, frequency, and length
predict the age of acquisition.

@@

For example, in the semantic domain, growth according to EXT could be
explained by a mechanism similar to cross-situational learning (McMurray
et al., 2012; Smith \& Yu, 2008; Yurovsky \& Frank, 2015). According to
this mechanism, children track the co-occurrence of concrete nouns with
their possible semantic referents. The referent of a word heard in only
one naming situation can be ambiguous (e.g., when the word
\enquote{ball} is heard for the first time in the presence of both a
ball and a chair), but hearing the same word in a diversity of semantic
contexts allows the learner to narrow down the set of possible
word-object mappings. In our case, free association (used to determine
semantic network connectivity) is related to contextual co-occurrence
(Fourtassi \& Dupoux, 2013; Griffiths, Steyvers, \& Tenenbaum, 2007),
meaning that highly connected words will tend to occur in a variety of
speech and referential contexts. This fact makes such words easier to
learn because they have more referential disambiguating cues across
learning contexts. Crucially, children can learn these words without
necessarily knowing the meaning of all other words with which they
co-occur (hence the similarity with EXT). This possibility is supported
by the finding that words' diversity of occurrence in child-directed
speech predicts their age of learning (Hills et al., 2010; Stella et
al., 2017).

In the phonological case, network growth according to EXT is also
compatible with a scenario whereby children are tracking low-level
statistical patterns, e.g., high probability sound sequences. Indeed,
connectivity in the phonological network is inherently correlated with
phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
is, highly connected words tend to be made of frequent sound sequences.
Children are sensitive to local phonotactic regularities (Jusczyk, Luce,
\& Charles-Luce, 1994), and this sensitivity might lead them to learn
higher-probability words more easily (Storkel, 2001). This explanation
is supported by computational simulations that show how learning general
phonotactics patterns create \enquote{well-worn paths} which allow the
models to represent several distinct but phonologically neighboring
words (Dell, Juliano, \& Govindjee, 1993; Siew, 2013; Takac, Knott, \&
Stokes, 2017). More generally, there is a growing interest in
investigating precisely how the local patterns acquired through
statistical learning may give rise to the global network organization
(For a review, see Karuza, Thompson-Schill, \& Bassett, 2016).

Besides using their own statistical learning skills, children could also
benefit from the way their caregivers speak. Perhaps the caregivers put
more emphasis on the words that are highly connected in \emph{their}
mature lexical network. This emphasis would guide children to learn
first these highly connected words, even though children do not have
access to the distribution of words' connectivity in the final network.
Investigating this possibility would require further research on
caregiver-child interaction (MacWhinney, 2014; B. C. Roy et al., 2015),
examining what words are introduced over development and the extent to
which children's uptake is influenced by this input (Clark, 2007; Hoff
\& Naigles, 2002; Huttenlocher et al., 1991).

This study investigated the class of nouns in isolation --- following
previous studies investigating the early semantic and phonological
network (Hills et al., 2009; Storkel, 2009). We could ask if studying
one class separately is a legitimate research strategy. In other words,
would word classes (such as nouns, verbs and function words) be acquired
relatively differently, or would they interact substantially to the
extent that it becomes unreasonable to study each class separately?

There are many observations that support the hypothesis that different
word classes have different pathways of learning, making it worthwhile
to study each class separately. For instance, different word classes
follow different time trajectories: In the early stages of development,
nouns tend to be acquired at a higher pace than predicates and function
words (Bates et al., 1994). Research has shown that this difference
cannot be trivially attributed to differences in the degree to which
these classes are present in the input; if anything, verbs and function
words are often more frequent in the input than nouns (e.g., Gentner,
1982). J. C. Goodman et al. (2008) found an effect of frequency on the
age of acquisition within --- not across --- classes. Further, recent
work by Braginsky et al. (2019) tested a large number of predictors,
besides frequency, and found that these predictors do not influence the
acquisition of word classes in the same way. For example, the
acquisition of nouns was found to be most influenced by frequency and
concreteness, whereas the acquisition of function words was most
influenced by word length.

This work shares a number of limitations with previous studies using
similar research strategy and datasets. Chief among these limitations is
the fact that the age of word acquisition is computed using different
children at different ages (due to the fact that available CDI data is
mainly cross-sectional). Such a measure has been shown to be valid and
reliable (Fenson et al., 1994), and has allowed researchers to study
important aspects of word learning (Braginsky et al., 2019; J. C.
Goodman et al., 2008; Hills et al., 2009; Stella et al., 2017; Storkel,
2009). In our case, the use of cost-effective cross-sectional data has
allowed us to leverage large-scale studies across several languages.
That said, it is important to remember that this type of data can only
inform us about the learning trajectory of the \enquote{average} child.
Although our study endorses, overall, the externally-driven account of
network growth, this does not mean individual children never use some
variant of INT or some combination of both INT and EXT (Beckage \&
Colunga, under review). To illustrate, some children develop
\enquote{islands of expertise,} that is, well-organized knowledge about
a certain topic (e.g., birds or dinosaurs). This prior knowledge enables
these children to learn new related words more easily (e.g., Chi \&
Koeske, 1983).

@@

We show in Figure \ref{fig:corrPlot} the correlation between the
phonological connectivity and age of acquisition in both comprehension
and production. The sparsity issue --- due to the low phonological
neighborhood in the children's lexicon --- is apparent: Most words had 0
connectivity, and a few had non-zero but small degrees. The values of
the correlations are much lower than the ones obtained with the
threshold of 2.
